---
title: "Ravi_ggplot with Error Bars-tv2"
output: html_document
---

Load Tidyverse Package
======================

```{r warning=FALSE}
library(tidyverse)
getwd()
```

```##Setup working directory```

```{r}
setwd("C:/Users/kchz694/OneDrive - AZCollaboration/From Desktop 8-5-20/RT R Scripts/R_scripts/TV_RMD")
getwd()
```

Read csv file from folder
```{r echo=FALSE}
tv2 <-read_csv("ex_tv2.csv") 
head(tv2)
```

Restructuring the Data
=============
Restructure tidy format from wide format to longer using pivot_longer. Columns gp1_1, gp1_2 etc. to grp (new variable, which can be used to split in the next step)and tumor values to tv

```{r}
tv2 <- tv2 %>% pivot_longer(cols =2:85, names_to="grp", values_to="tv")
head(tv2)
```
Now using separate func __split__ **grp** into *grp* and _replicate_ to get replicate number separate at and remove *_*

```{r}
tv2 <- tv2 %>% separate(grp, into=c("grp","replicate"),sep="_")
head(tv2,10)
```
Clean up the NA values which got from the blank lines on the original data

```{r}
tv2 %>%
  filter(!is.na(tv)) -> tv2

head(tv2)
```
To show how paste0 works
 ```paste0``` so it doesn't put a space between the two parts.
```{r}
paste0("gp",1:14)
```

Need convert grp in to factor becoz in the legend grp numbers shows in the alphabetical order (ex: gp1, gp10,gp11,gp2,etc.To avoid this confusion convert grp into levels using factor func. Join(paste) together ```Gp``` to an ordered numerical vector.

```{r}
tv2 %>%
  mutate(grp = factor(grp, levels=paste0("gp",1:14))) -> tv2
head(tv2)
```
GGPlot summarisation (instead of manual):
====================
Add summarisation to ```geom_line```.
Use ```stat_summary``` and add errorbar/point.This defaults to using SEM

```{r}
tv2 %>%
  ggplot(aes(x=Day,y=tv,color=grp)) +
 
  geom_line(stat="summary", fun="mean")+
  stat_summary(geom="errorbar", width=2.0)+
  stat_summary(geom="point", width=0.5)+
  #geom_point(width=0.5)+ =need to add in the stat_summary
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  coord_cartesian(ylim=c(0,2000))+
  scale_x_continuous(breaks=c(20,40,60,80,100,120,140))+
  xlab("Days")+
  ylab("TV mm3")
```

ALL the code same place and use for plotly()
geom_line(stat="summary", fun="mean")+ # need to use after stat_summary(), geom_point in order to show lines in the graph

```{r}

rtplot <- tv2 %>%
  ggplot(aes(x=Day,y=tv,color=grp)) +
  
  stat_summary(geom="errorbar", width=2.0)+
  stat_summary(geom="point", width=0.5)+
  geom_line(stat="summary", fun="mean")+
   #geom_point(width=0.5)+ =need to add in the stat_summary
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  coord_cartesian(ylim=c(0,2000))+
  scale_x_continuous(breaks=c(20,40,60,80,100,120,140))+
  xlab("Days after Tumor Cells Implant")+
  ylab("TV mm3") 

rtplot     
   
```



```{r}
library(plotly)
rtplot1 <- ggplotly(rtplot)     
rtplot1  
```








